Analysis

### 2023-04-10 Analysis.rmd
experts and non-experts using Rt

>>>>

# number of experts and non-experts who used Rt forecasts
nums |>
  group_by(forecast_date, target_type, expert, method) |>
  summarise(n = n()) |>
  group_by(target_type, expert, method) |>
  summarise(
    mean = mean(`n`), 
    median = median(`n`), 
    min = min(`n`), 
    max = max(`n`)
  )
exp_method

# proportion of experts and non-experts using Rt
nums |>
  group_by(forecast_date, target_type, expert, method) |>
  summarise(n = n()) |>
  #calculate proportion
  group_by(forecast_date, target_type, expert) |>
  mutate(n = n / sum(n)) |>
  group_by(expert, method) |>
  summarise(
    mean = mean(`n`), 
    median = median(`n`), 
    min = min(`n`), 
    max = max(`n`)
  ) |>
  filter(method == "Rt")
